How to Write Theses\\ With Two Line Titles

### 2020-04-15 chapters/introduction/introduction.tex
New

Machine learning algorithms are gaining rapid popularity 
Testing 
Oracle problem
In this paper we first introduce metamorphic testing. Then identify new metamorphic properties for image datasets.

Machine learning has gained rapid popularity in the past decade and different sectors like healthcare, finance, retail, etc. are using machine learning techniques to provide better products and services. This rising popularity has created a demand for better implementation of the state-of-the-art algorithms in order to implement more complex and sophisticated use cases. Machine learning algorithms has been around for a long time now and several developers have written a number of tools and libraries to help others learn and use these algorithms in their own projects.  While developing and training a machine learning model, the developers rely on the accuracy of these libraries to produce best results where the aim is to create a model that makes the best predictions.
Conventionally, oracles have been used to test the correctness of a program. Oracles provide expected values against which the output from the program can be compared and validated. Lack of reliable oracles for testing machine learning algorithms makes it very hard to test the accuracy of such programs. This problem is called the oracle problem\cite{Weyuker}. Oracle problem arises when either:
\begin{itemize}
  \item An oracle does not exist, or,
  \item An oracle can theoretically exist but it is computationally too expensive to determine the output.
\end{itemize}
Such set of programs which does not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Weyuker}. Davis and Weyuker describe these programs as \enquote{Programs which were written in order to determine the answer in the first place. There would be no need to write such programs if the correct answer were known}\cite{Davis1981}. Most machine learning programs fall under this category as they are written in order to predict the correct answers in the first place. Several techniques can be employed to verify the correctness of such programs. One of the most popular methods being the use of pseudo-oracles. To use pseudo-oracle two or more implementations of the algorithm are independently developed to fulfill the same specification. They are run on the same input test data and the outputs from them are then compared. If the outputs match it can be asserted that the original results are according to the specification. This kind of testing is often referred to as dual coding. However, this technique introduces a significant overhead in terms of implementing two or more versions of the same algorithm and testing their outputs and is more suitable for mission-critical systems\cite{Weyuker}.\newline

Another testing methodology called Metamorphic testing introduced by Chen et. al can be used for testing ML programs instead. It addresses some of these problems while testing the \enquote{non-testable programs} without significant overhead. The idea behind Metamorphic testing is that it easier to compare and understand the relationship between outputs than to compare and understand input-output behavior. For a prototype example: To test a program which implements the $sin$ function, the output from the program for value of $sin$ at $x$ could be compare to the real value of $sin(x)$ or, the mathematical property of $sin(x) = sin(\pi-x)$ can be exploited to verify the correct implementation of $sin$ function. Such relation $(sin(x) = sin(\pi-x))$ are called Metamorphic Relations. Metamorphic testing makes use of metamorphic relations where an input relation is used to generate new input test cases from existing test data, and an output relation is used to compare the outputs produced by the test cases.\newline
In this paper, we will explore the types of guarantees one can expect a machine learning model to possess because of the properties that the underlying algorithm of the implementation.
% In particular we will look at google's tensorflow.
% Dataset coverages
% and
% We propose applying MT as a way of testing and verifying ML programs.

@@

In this study we will answer the following research questions:
\begin{enumerate}
%   \item How does metamorphic testing compare to other testing methodologies for testing machine learning algorithms?
  %\item Can we quantify reliability of predictions made by machine learning algorithms?
    \item Identify metamorphic properties that can be used to generate new test data from image datasets.
%   \item How does metamorphic properties affect different dataset and deep-learning algorithms?
    \item Does metamorphic properties have similar affect on the individual classes in a dataset.
    \item What range of metamorphic transformation produce similar accuracy as the original dataset?
    % \item Are some machine-learning algorithms more robust than others?

%   \item How sensitive are the predictions made by ML algorithms to the change in input data?
%   \item At what point does the algorithm fail to produce correct classifications on distorted inputs?

\end{enumerate}
%Point of failure. by humans& computer. (visual inpection)
%Properties of ML affect
%

>>>>

% Machine learning algorithms are gaining rapid popularity 
% Testing 
% Oracle problem.
% In this paper we first introduce metamorphic testing. Then identify new metamorphic properties for image datasets.

Machine learning has gained rapid popularity in the past decade, and different sectors like healthcare, finance, retail, etc. are using machine learning techniques to provide better products and services. This rising popularity has created a demand for better implementation of the state-of-the-art algorithms in order to implement more complex and sophisticated use cases. Machine learning algorithms have been around for a long time now, and several developers have written a number of tools and libraries to help others learn and use these algorithms in their own projects.  While developing and training a machine learning model, the developers rely on the accuracy of these libraries to produce the best results where the aim is to create a model that makes the best predictions.
Conventionally, oracles have been used to test the correctness of a program. Oracles provide expected values against which the output from the program can be compared and validated. Lack of reliable oracles for testing machine learning algorithms makes it very difficult to test the accuracy of such programs. This problem is called the oracle problem\cite{Weyuker}. Oracle problem arises when either:
\begin{itemize}
  \item An oracle does not exist, or,
  \item An oracle can theoretically exist, but it is computationally too expensive to generate/use it.
\end{itemize}
Such a set of programs that do not have a test oracle to predict the output on a set of inputs are called \enquote{non-testable programs}\cite{Weyuker}. Davis and Weyuker describe these programs as \enquote{Programs, which were written in order to determine the answer in the first place. There would be no need to write such programs if the correct answer were known}\cite{Davis1981}. Since most machine learning programs are developed to determine the correct answers in the first place, most of them fall under this category. Nevertheless, several techniques can be employed to verify the correctness of such programs. One of the most popular methods is the use of pseudo-oracles. In order to use pseudo-oracle, two or more implementations of the algorithm are independently developed, which fulfill the same specification. They are run on the same input test data, and their outputs are compared. If the outputs match it can be asserted that the original results are according to the specification. This kind of testing is often referred to as dual coding. Nevertheless, this technique introduces significant overhead in terms of implementing two or more versions of the same algorithm and testing their outputs. This can lead to significant computation and financial costs. However, dual coding is more suitable for mission-critical systems\cite{Weyuker}.
\newline

Chen et al. introduced another method of testing these machine learning programs with no oracle called Metamorphic testing. It addresses some of those problems while testing the \enquote{non-testable programs} without significant overhead. The idea behind Metamorphic testing is that it is easier to compare and understand the relationship between outputs than to compare and understand input-output behavior. For example: To test a program which implements the $sin$ function, the output from the program for value of $sin$ at $x$ could be compare to the real value of $sin(x)$ or, we can exploit the the mathematical property of $sin(x) = sin(\pi-x)$ to verify the correct implementation of $sin$ function. Mathematical properties like $(sin(x) = sin(\pi-x))$ are called "Metamorphic Relations" and, metamorphic testing makes use of metamorphic relations where an input relation is used to generate new input test cases from existing test data. An output relation is also used to compare the outputs produced by the new test cases.
\newline
In this paper, we will explore some new properties which can be used with image datasets in particular, and we will also test them on some standard machine learning algorithms.
% In particular we will look at google's tensorflow.
% Dataset coverages
% and
% We propose applying MT as a way of testing and verifying ML programs.

@@

In this study we will answer the following research questions:
\begin{enumerate}
%   \item How does metamorphic testing compare to other testing methodologies for testing machine learning algorithms?
  %\item Can we quantify reliability of predictions made by machine learning algorithms?
    \item Identify metamorphic properties that can be used to generate new test data from image datasets.
%   \item How does metamorphic properties affect different dataset and deep-learning algorithms?
    \item Do metamorphic transformations have a similar effect on all the classes in a dataset?
    \item What range of metamorphic transformation produces similar accuracy as the original dataset?
    % \item Are some machine-learning algorithms more robust than others?

%   \item How sensitive are the predictions made by ML algorithms to the change in input data?
%   \item At what point does the algorithm fail to produce correct classifications on distorted inputs?
\end{enumerate}
We will also investigate the robustness of some machine learning algorithms that we implement to test our transformed datasets.
%Point of failure. by humans& computer. (visual inpection)
%Properties of ML affect
%

### 2020-04-15 chapters/litReview/finalLit.tex
New

\section{Software testing}
Testing is one of the most important activity in software development life cycle. Bertolino \cite{Bertolino2007} define software testing as, ``observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions.'' Testing is widely used in industry for various quality assurance purposes. Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure continuous service, etc.\cite{Bertolino2007} A study by Beizer \cite{Beizer1990} has estimated that software testing can use up to fifty percent, or more, of the total development cost. Thus, it is clear that program software testing is worthy of our attention for research and improvement \cite{Beizer1990}.
Weyuker \cite{Weyuker} categorizes the testing research activities into three categories:
\begin{enumerate}
  \item Develop a sound theoretical basis for testing.
  \item Devise and improve testing methodologies, especially the mechanizable ones.
  \item Define accurate measurement criteria for testing data adequately.
\end{enumerate}

However,  there are a lot of uncertainties in program testing and it is often not so straightforward to test programs. These Uncertainties in most systems are introduced by either human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments. In the context of software testing, the two very obvious fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle \cite{Chen2002,Elbaum2014}.
Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used. While performing mathematical computations, errors from three sources can creep in \cite{Weyuker}:
\begin{enumerate}
  \item The mathematical model used to do the computations.
  \item Programs written to implement the computation.
  \item The features of the environment like round-off, floating point operations etc.
\end{enumerate}

 One of the first problems that testers run into while testing these uncertain programs is that they don't have access to acceptable output to test the program's predictions against. This problem is often referred to as the Oracle problem. Weyuker \cite{Weyuker} provides founding definition of an oracle as "a system that determines the correctness of the solution by comparing the system's output to the one that it predicts". She also defines non-testable programs as the programs for which such oracles do not exist. The term non-testable is used, from the point of view of correctness testing. If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.

 A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles. If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault. On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time \cite{Elbaum2014}.

 Many techniques have since been developed to test these set of non-testable programs. One way of elevating the oracle-problem is through the use of pseudo oracle. It is also referred to as dual-coding and is used in highly critical software \cite{Weyuker,Murphy2009}. Pseudo-oracles are multiple implementation of same specification of the original program under test.
 However, dual coding comes with it's own set of problems. As the authors Weyuker \cite{Weyuker} and Murphy, Shen, and, Kaiser \cite{Murphy2009} pointed out some limitations that pseudo-oracles require at least two implementation and it may come out to be a lot of overhead or, multiple implementation may not exist or, the multiple implementation may be created by the same or same set of developers prone to make same mistakes.
 In light of these shortcomings of the testing process Weyuker \cite{Weyuker} finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.

Due to a great deal of overhead involved, pseudo-oracles may not be practical for every situation.  
A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined. The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases. In this case, we are deliberately omitting test cases even though these cases may have been identified as important. They are not being omitted because it is not expected that they will yield substantial additional information, but rather because they are impossible, too difficult, or too expensive to check. The problem with using simple test cases is very obvious i.e. it is common for central cases to work perfectly whereas boundary cases to cause errors. \cite{Weyuker}

>>>>

\section{Software testing}
Testing is one of the most crucial activities in the software development life cycle. Bertolino \cite{Bertolino2007} define software testing as, \enquote{observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions}. Software testing is a very common practice in the software industry and is used to ensure the quality of the product. Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure continuous service, etc.\cite{Bertolino2007} A study by Beizer \cite{Beizer1990} has estimated that software testing can use up to fifty percent, or more, of the total development cost. Thus, it is clear that program software testing is worthy of our attention for research and improvement \cite{Beizer1990}.\\
Weyuker \cite{Weyuker} categorizes the testing research activities into three categories:
\begin{enumerate}
  \item \enquote{Develop a sound theoretical basis for testing}.
  \item \enquote{Devise and improve testing methodologies, especially the mechanizable ones}.
  \item \enquote{Define accurate measurement criteria for testing data adequately}.
\end{enumerate}

However,  there are a lot of uncertainties in program testing, and it is often not so straightforward to test programs. These uncertainties in most systems are introduced by either human biases, non-deterministic machine learning algorithms, external libraries, or sensing variability. This complexity emerges due to the need to support deep interactions between interconnected software systems, execution environments, and their users. In the context of software testing, the two very fundamental problems are increased uncertainty of what makes up the input space and what is considered as acceptable behavior in the absence of an oracle \cite{Chen2002,Elbaum2014}.

Although non-testable programs occur in all areas of software engineering, the problem is undoubtedly most acute in areas where mathematical computations are performed, particularly where floating-point computation is involved. While performing mathematical computations, errors from three sources can creep in \cite{Weyuker}:

\begin{enumerate}
  \item The mathematical model used to do the computations.
  \item Programs written to implement the computation.
  \item The features of the environment like round-off, floating point operations etc.
\end{enumerate}

 One of the first problems that testers run into while testing these uncertain programs is that they do not have access to acceptable outputs against which the program's predictions can be compared. The lack of access to correct output is often referred to as the Oracle problem. Weyuker \cite{Weyuker} provides the founding definition of an oracle as \enquote{a system that determines the correctness of the solution by comparing the system's output to the one that it predicts}. She also defines non-testable programs as the programs for which such oracles do not exist. If a tester cannot agree on the output of a program or has to spend a tremendous amount of resources to find the correctness of the results, testing those systems may not be worth it. Thus the term non-testable is used from the point of view of correctness testing.

 Many techniques have since been developed to test these sets of non-testable programs. One way of elevating the oracle-problem is by using pseudo oracles. It is also referred to as dual-coding and is used in highly critical software \cite{Weyuker,Murphy2009}. Pseudo-oracles are multiple implementations of the same specification of the original program under test.
 However, dual coding comes with its own set of problems. As the authors Weyuker \cite{Weyuker} and Murphy, Shen, and, Kaiser \cite{Murphy2009} pointed out some limitations of pseudo-oracles include the use of least two implementations, which may come out to be a lot of overhead or, multiple implementations may not exist or, the multiple implementations may be created by the same or same set of developers prone to make same mistakes.
 In light of these shortcomings of the testing process Weyuker \cite{Weyuker} finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item \enquote{The criteria used to select the test data.}
  \item \enquote{The degree to which the criteria were fulfilled.}
  \item \enquote{The test data, the program ran on.}
  \item \enquote{The output of each of each test datum.}
  \item \enquote{How the results were determined to be correct or acceptable.}
\end{enumerate}
Although these recommendations do not solve the problem of lack of oracle, however, they do provide information on whether the program should be considered adequately tested or not.

Due to a great deal of overhead involved, pseudo-oracles may not be practical for every situation.  
% A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined. The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases. In this case, we are deliberately omitting test cases even though these cases may have been identified as important. They are not being omitted because it is not expected that they will yield substantial additional information, but rather because they are impossible, too difficult, or too expensive to check. The problem with using simple test cases is very obvious i.e. it is common for central cases to work perfectly whereas boundary cases to cause errors. \cite{Weyuker}

Another course of action that is used often in these situations is to test the program on "simplified" test data for which the correct output can be easily determined. Testers can then extrapolate the results for more complex cases from the output of the "simplified" test data. However, not all test cases can be generated with this technique. This deliberate omission of even the important test cases is because they might be too difficult, if not, impossible to check and not because they are not expected to yield useful information. The second problem with using simple test cases is very obvious i.e. it is normal for central and simple cases to work perfectly, whereas edge cases that may be ignored tend to cause errors. \cite{Weyuker}

 Developing sophisticated oracles is another way of encountering the oracle problem. If the oracles are very relaxed such that they tolerate the effects of uncertainties, then there is a chance that a fault may be masked. On the other hand, f the oracles are too narrow, it may cause them to generate false positives, resulting in wasted developer's time \cite{Elbaum2014}.

### 2020-04-15 chapters/litReview/mlAlgo.tex
New

\section{Overview of Machine Learning Algorithms}
\subsection{Neural network}
Neural networks were first introduced in 1944 by two University of Chicago researchers Warren McCullough and Walter Pitts, who later moved to MIT in 1952. These algorithms are modeled loosely after the human brain, that are designed to recognize patterns.  Dr. Robert Hecht-Nielsen, inventor of the first neurocomputer defines a neural network as:
"...a computing system made up of a number of simple, highly interconnected processing elements, which process information by their dynamic state response to external inputs"\cite{Caudill}.
\begin{figure}[htb!]
    \centering
    \includegraphics[scale=0.15]{files/nn.png}
    \caption{Neural network}
    \label{Neural network}
    \end{figure}
    \FloatBarrier
% cite figure: https://towardsdatascience.com/applied-deep-learning-part-1-artificial-neural-networks-d7834f67a4f6
A typical neural network looks like a variation of Figure \ref{Neural network}. \\
Input layer: The leftmost layer in the network is made up of input neurons and the layer is called the input layer. There is no computation performed in the nodes at this layer. Input layer simply provides the information from the environment to the next layer.
Hidden layers: The layers in the middle make up the hidden layers, as the neurons in these layers are neither inputs nor outputs. There can be zero or multiple hidden layers. Hidden layers takes the input from the input layer and passes information to the output layer after performing computation on the data. 
Output layer: The rightmost or output layer contains the output neurons, or, as in this case, a single output neuron. 
There are no set rules to design the layers of a neural network (specially the hidden layers) and this process is often considered as an art\cite{NN}. We determine the number of hidden layers and nodes empirically for each particular case in order to optimize performance. The edges (or connections) between a layer and the layer before it are represented by a weight $\omega_{ij}$, which represents the strength of connection between i and j nodes. During the training phase of the neural network, we assign random values to the weights for each connection. The algorithm then tries to optimize the weights so that the error function is minimized. For each node at a layer all the output from the previous node is multiplied by the weight of connections between them and the sum of all the different connections produces the value at that node. This cycle is repeated for all the nodes in every layer. The algorithm compares the prediction from the output layer to the real value and readjusts the weights. Once the optimal value is reached the network can be used to make predictions\cite{hall199}.

These neural networks where the output from one layer is used as input to the next layer are called feedforward neural networks\cite{NN}\cite{hall199}. There are no loops in the feedforward neural network and the information flows in one direction and are never fed back. The most well known form of a feed forward neural network is called multilayer perceptron(MLP). MLPs are also called universal function approximator. A single hidden layer MLP with a sufficient number of nonlinear units can act as a continuous function on to a narrow input domain with arbitrary precision. \cite{Graves}.
There are some other models of artificial neural networks in which feedback loops are possible. These models are called recurrent neural networks. The idea in these models is to have neurons which fire for some limited duration of time, before becoming quiescent. That firing can stimulate other neurons, which may fire a little while later, also for a limited duration. That causes still more neurons to fire, and so over time we get a cascade of neurons firing. Loops don't cause problems in such a model, since a neuron's output only affects its input at some later time, not instantaneously. Recurrent neural nets have been less influential than feedforward networks, in part because the learning algorithms for recurrent nets are (at least to date) less powerful. But recurrent networks are still extremely interesting. They're much closer in spirit to how our brains work than feedforward networks. And it's possible that recurrent networks can solve important problems which can only be solved with great difficulty by feedforward networks.\cite{NN} % cite: http://neuralnetworksanddeeplearning.com/chap1.html

\subsection{Convolutional neural network}
Convolutional neural networks (ConvNet) are very similar to ordinary neural networks in structure. They work by extracting simple features at a higher resolution and then converting them into more complex features at a coarser resolution \cite{simard2003best}. It does so by performing dot product on the inputs received at each neuron and optionally follow it with non-linearity. Just like a normal neural network, convolutional neural network (from the input image to output class) can be expressed as a single differential function. It also has a loss function on the fully-connected output layer and the neurons have learnable weights and biases which are optimized during the learning phase.

What makes it different from an ordinary neural network is the architecture of a ConvNet. It makes explicit assumption that the inputs are images, which allows us to encode certain properties into the architecture. In particular, unlike a regular Neural Network, the layers of a ConvNet have neurons arranged in 3 dimensions: width, height, depth. A simple ConvNet is a sequence of layers and every layer transforms one volume of activation to another through a differentiable function.

@@

A ConvNet architecture is made up of the following layers and these layers are stacked to form the full network \cite{krizhevsky2012imagenet}: \\
Input layer: This layer holds the raw input image in form of it's pixel values and color channels.\\
Convolutional layer (Conv): This layer computes the dot product between it's weight and a small region in the previous layer it is connected to. It is a linear operation which multiplies the input from the previous layer to a two-dimensional array of weights called filter or kernel. \\
Rectified linear unit (ReLu): This layer applies an element-wise activation function, like $max(0,x)$ with the threshold at zero. It introduces non-linearity to the system which has just been doing linear computations (element wise multiplication and sum) in previous Conv layers. \\
Pooling layer (POOL): This layer performs a downsampling operation along the spatial dimensions. This helps in two major ways: $i)$ The amount of parameters or weights is reduced by 75\%. $ii)$ It also reduces the problem of overfitting.\\
Fully connected layer (FC): The fully connected output layer computes the class scores for the input. The neurons in this layer are connected to every neuron in the previous layer. The only difference between this layer and the Conv layer is that the neurons in Conv layer are only connected to a local region in the input layer and the neurons in Conv layer share parameters. The neurons in both the layer compute dot product and their function form is identical. Thus, it is easily possible to convert between the fully connected and Conv layer.\\

It should be noted that some layers contain parameters while others may not. The ReLu/Pool layer implements a fixed function whereas, the Conv/FC layers transformation functions work on the activations in the input volume and the weights and biases of the neurons. The parameters in Conv/FC layer is trained using gradient descent such that the scores computed by ConvNet is consistent with the expected output of each image in the training set \cite{convNNStan}.
%cite http://cs231n.github.io/convolutional-networks/

>>>>

\section{Overview of Machine Learning Algorithms}
\subsection{Neural network}
Neural networks were first introduced in 1944 by two University of Chicago researchers Warren McCullough and Walter Pitts. The neural network algorithms are modeled loosely after the human brain, which is very efficient in pattern recognition.  Dr. Robert Hecht-Nielsen, who also invented the first neurocomputer, defines a neural network as:
"...a computing system made up of a number of simple, highly interconnected processing elements, which process information by their dynamic state response to external inputs"\cite{Caudill}.
\begin{figure}[htb!]
    \centering
    \includegraphics[scale=0.15]{files/nn.png}
    \caption{Neural network}
    \label{Neural network}
    \end{figure}
    \FloatBarrier
% cite figure: https://towardsdatascience.com/applied-deep-learning-part-1-artificial-neural-networks-d7834f67a4f6
A typical neural network looks like a variation of Figure \ref{Neural network} and is composed of the following layers. \\
Input layer: This is the leftmost layer in the network. It is made up of input neurons, and the layer is called the input layer. There is no computation performed in the nodes at this layer. The input layer simply provides information from the environment to the next layer. \\
Hidden layers: The layers in the middle make up the hidden layers. As the name suggests, these layers are neither inputs nor outputs. There can be zero or multiple hidden layers. Hidden layers take the input from the input layer and pass the information to the output or other hidden layer after performing computation on the data. \\
Output layer: The last layer in the neural network is called the output layer. This layer contains the output neurons, which tells the final class of the input. In the example above, we have a single output neuron. \\

% There are no set rules to design the layers of a neural network (specially the hidden layers) and this process is often considered as an art\cite{NN}. The number of hidden layers and nodes are often determined empirically for each particular case in order to optimize performance. The edges (or connections) between a layer and the layer before it are represented by a weight $\omega_{ij}$, which represents the strength of connection between i and j nodes. During the training phase of the neural network, we assign random values to the weights for each connection. The algorithm then tries to optimize the weights so that the error function is minimized. For each node at a layer all the output from the previous node is multiplied by the weight of connections between them and the sum of all the different connections produces the value at that node. This cycle is repeated for all the nodes in every layer. The algorithm compares the prediction from the output layer to the real value and readjusts the weights. Once the optimal value is reached the network can be used to make predictions\cite{hall199}.
There are no set rules to design the layers of a neural network (especially the hidden layers), and this process is often considered as an art\cite{NN}. The number of hidden layers and nodes is often determined empirically for each particular case in order to optimize performance. The edges (or connections) between two layers($i$ and $j$) are represented by weight $\omega_{ij}$, which represents the strength of the connection between $i$ and $j$ nodes. When the neural network is being trained, we assign random values to the weights for each connection. The weights are then optimized such that the error function is minimized. For each node at a layer, all the outputs from the previous nodes are multiplied by the weight of connections between them. The weighted outputs are then summed and used as the value at that node. This cycle is repeated for all the nodes in every layer. The algorithm compares the prediction from the output layer to the real value and readjusts the weights. Once the optimal value is reached, the network can be used to make predictions\cite{hall199}.

These neural networks where the input of a layer is received from the output of the previous layer are called feedforward neural networks\cite{NN}\cite{hall199}. The feedforward neural network has no loops, and the information flows in one direction and is never fed back. The most well-known form of a feedforward neural network is called a multilayer perceptron(MLP). MLPs are also called universal function approximator. An MLP with one hidden layer and a sufficient number of nonlinear units can act as a continuous function on a narrow input domain with arbitrary precision \cite{Graves}.
Other models of artificial neural networks where a feedback loop is possible are called recurrent neural networks. The neurons in these networks fire for a limited duration of time before becoming dormant. However, the firing stimulates other neurons in the network, which may fire after some time for a limited duration of time. This can have a cascading effect causing yet other neurons to fire later. Having loops in these models does not create problems since the neurons firing does not affect their input instantly but at a later time. Even though the recurrent neural networks are much similar to our brains than feedforward networks, they have not been as influential as the feedforward networks. This is mostly because the learning algorithms for recurrent nets are (at least to date) less powerful than feedforward networks. In the future, it will be possible that the recurrent networks will be able to solve significant problems which feedforward networks solve with great difficulty.\cite{NN}
% cite: http://neuralnetworksanddeeplearning.com/chap1.html

\subsection{Convolutional neural network}
% Convolutional neural networks (ConvNet) are very similar to ordinary neural networks in structure. They work by extracting simple features at a higher resolution and then converting them into more complex features at a coarser resolution \cite{simard2003best}. It does so by performing dot product on the inputs received at each neuron and optionally follow it with non-linearity. Just like a normal neural network, convolutional neural network (from the input image to output class) can be expressed as a single differential function. It also has a loss function on the fully-connected output layer and the neurons have learnable weights and biases which are optimized during the learning phase.

% What makes it different from an ordinary neural network is the architecture of a ConvNet. It makes explicit assumption that the inputs are images, which allows us to encode certain properties into the architecture. In particular, unlike a regular Neural Network, the layers of a ConvNet have neurons arranged in 3 dimensions: width, height, depth. A simple ConvNet is a sequence of layers and every layer transforms one volume of activation to another through a differentiable function.
Convolutional neural networks (ConvNet) are very similar to the conventional neural networks in terms of structure.  They work by extracting simple features at a higher resolution and transforming them into more complex features at a more granular resolution \cite{simard2003best}. It does so by performing dot product on the inputs received at each neuron and optionally follow it with non-linearity. Just like a typical neural network, ConvNets (from the input image to output class) can be represented with a single differential function. The neurons in ConvNets have learnable weights and biases, which are optimized during the learning phase.  It also has a loss function on the fully-connected output layer, which is minimized.

What makes it different from an ordinary neural network is the architecture of a ConvNet. It makes very specific assumptions that the inputs are images, which allows us to encode specific properties into the architecture. In particular, unlike a regular Neural Network, the neurons in the layers of a ConvNet are arranged in 3 dimensions: width, height, depth. A simple ConvNet is a sequence of layers, and every layer transforms one volume of activation to another through a differentiable function.

@@

% A ConvNet architecture is made up of the following layers and these layers are stacked to form the full network \cite{krizhevsky2012imagenet}: \\
% Input layer: This layer holds the raw input image in form of it's pixel values and color channels.\\
% Convolutional layer (Conv): This layer computes the dot product between it's weight and a small region in the previous layer it is connected to. It is a linear operation which multiplies the input from the previous layer to a two-dimensional array of weights called filter or kernel. \\
% Rectified linear unit (ReLu): This layer applies an element-wise activation function, like $max(0,x)$ with the threshold at zero. It introduces non-linearity to the system which has just been doing linear computations (element wise multiplication and sum) in previous Conv layers. \\
% Pooling layer (POOL): This layer performs a downsampling operation along the spatial dimensions. This helps in two major ways: $i)$ The amount of parameters or weights is reduced by 75\%. $ii)$ It also reduces the problem of overfitting.\\
% Fully connected layer (FC): The fully connected output layer computes the class scores for the input. The neurons in this layer are connected to every neuron in the previous layer. The only difference between this layer and the Conv layer is that the neurons in Conv layer are only connected to a local region in the input layer and the neurons in Conv layer share parameters. The neurons in both the layer compute dot product and their function form is identical. Thus, it is easily possible to convert between the fully connected and Conv layer.\\
A ConvNet architecture is made up of the following layers. The full network is made of multiple instances of these layers stacked one after other \cite{krizhevsky2012imagenet}: \\
Input layer: This layer contains the raw input image in the form of its pixel values and color channels.\\
Convolutional layer (Conv): This layer calculates a dot product between its assigned weights and a small region in the previous layer it is connected to. It is a linear operation that multiplies the input from the previous layer to a two-dimensional array of weights called filter or kernel. \\
Rectified linear unit (ReLu): This layer applies an element-wise activation function, like $max(0,x)$ with the threshold at zero. The purpose of this layer is to introduce non-linearity to a system, which has just been doing linear computations (element-wise multiplication and sum) so far. \\
Pooling layer (POOL): This layer performs a downsampling operation along the spatial dimensions. This helps in two major ways: $i)$ The amount of parameters or weights is reduced by 75\%. $ii)$ It also reduces the problem of overfitting.\\
Fully connected layer (FC): The fully connected output layer is used to compute the class scores for an input. The only difference between this layer and the Conv layer is that the neurons in the Conv layer are only connected to a local region in the input layer while the neurons in the FC layer are connected to every neuron in the previous layer. The neurons in both the layer compute dot product, and their function form is identical. Thus, it is easily possible to convert between the fully connected and Conv layer.\\

It should be noted that some layers have parameters, while others may not. The ReLu/Pool layer implements a fixed function, whereas the Conv/FC layers transformation functions work on the activations in the input volume and the parameters (weights and biases) of the neurons. During the training period, the weights and biases of the Conv/FC layer are trained using gradient descent. The parameters are trained such that the scores computed by ConvNet generate outputs that match the expected output of each image in the training set \cite{convNNStan}.
% It should be noted that some layers contain parameters while others may not. The ReLu/Pool layer implements a fixed function whereas, the Conv/FC layers transformation functions work on the activations in the input volume and the weights and biases of the neurons. The parameters in Conv/FC layer is trained using gradient descent such that the scores computed by ConvNet is consistent with the expected output of each image in the training set \cite{convNNStan}.
%cite http://cs231n.github.io/convolutional-networks/
